Complete Workload Analysis of Real Autonomous Driving System: Apollo, Baidu Inc.

### 2019-04-18 paper/template/conference_041818.tex
Added text to the introduction

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{abstract}
    Autonomous driving is a field that gathers many interest from the academics world and from industry leaders.\\
    The software of an autonomous driving systems (ADS) incorporates the state-of-the-art from many disciplines, such as computer vision, robotics, geolocalization.
    Although the high level architecture of an autonomous driving system and the main algorithms used are known, the complete analysis of a real ADS is still difficult, especially for what concerns the modules interdependencies, interactions, either software and hardware, and pre- and post-processing.\\
    In this paper, we want to extract those point of views and quantify them according different architectural aspects: response times, memory movements, complexity and CPU-GPU relationship.\\
    The analysis is based on the open-source Apollo ADS developed by Baidu and is focused on the most important modules: perception, prediction and planning.
\end{abstract}

@@

Response time \cite{b1} is crucial for the predictability and accuracy of the system, especially when multiple sensor and components are present, each of them with a processing routine associated.
The maximum response time, that has been adopted as standard in the field of autonomous driving, is 100 ms and should ensure a proper and safe reaction to any possible situation.
Several processing routines use time deltas to perform corrections and projections of input and if those time-deltas are exceeding context-related thresholds then the input is discarded, losing some potential useful information, so limiting the response time will affect also the accuracy of the system.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{float}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{dblfloatfix}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{abstract}
    Autonomous driving is a field that gathers many interest from the academics world and from industry leaders.\\
    The software of an autonomous driving systems (ADS) incorporates the state-of-the-art from many disciplines, such as computer vision, robotics, geo-localization.
    Although the high level architecture of an autonomous driving system and the main algorithms used are known, the complete analysis of a real ADS is still difficult, especially for what concerns the modules interdependencies, interactions, either software and hardware, and pre- and post-processing.\\
    In this paper, we want to extract those point of views and quantify them according different architectural aspects: response times, memory movements, complexity and CPU-GPU relationship.\\
    The analysis is based on the open-source Apollo ADS developed by Baidu and is focused on the most important modules: perception, prediction and planning.
\end{abstract}

@@

Response time \cite{b1} is crucial for the predictability and accuracy of the system, especially when multiple sensors and components are present, each of them with a processing routine associated.
The maximum response time, which has been adopted as standard in the field of autonomous driving, is 100 ms and should ensure a proper and safe reaction to any possible situation.
Several processing routines use time deltas to perform corrections and projections of input and if those time-deltas are exceeding context-related thresholds then the input is discarded, losing some potential useful information, thus limiting the response time will affect also the accuracy of the system.

Apollo is a modular data-driven ADS, containing several modules, each of them pursues an high level feature of autonomous driving, such as perception, prediction, planning, control, localization.
Modules can be treated as black boxes and described in terms of input/output relationships.
This characterization enables the analysis of modules independently, provided that the inputs fed are feasible.
Modules are further expressed in terms of set of components, which represent lower level tasks.
Each component follows the same paradigm of modules, which means interactions within a module are based on input/output relationships through a publisher and subscriber architecture.

Cyber is the Apollo's runtime framework that implements the communication among components.
The publisher and subscriber communication adopted by Cyber is based on channels and messages.
Messages are serialized objects, using the Google's Protocol Buffer, which then are broadcast on channel(s).
Each component can be a reader or writer of multiple channels at the same time.

Apollo supports multiple sensors, different prediction evaluators and several scenario-based planners.
This rich environment carries out the need of having the right hardware equipment to support each task.
CPU should be able to sustain many multi-threaded algorithms and provides enough cores to execute several processes concurrently.
GPU is required for the execution of convolutional neural networks (CNN), vector and matrix operations, which are especially encountered in the perception module.

\begin{figure}[htb]

    \centering
    \includegraphics[width=0.5\textwidth]{images/apollo_software_architecture.png}
    \caption{Apollo Software Architecture}
    \label{}
\end{figure}

\clearpage
